A Graph-based Framework for Coverage Analysis in Autonomous Driving

### 2025-10-17 article/article.tex
subgraph isomorphism plots

\documentclass{article}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{graphicx}

\title{A Graph-based Framework for Coverage Analysis in Autonomous Driving}
\author{xxx}
\date{\today}

@@

test3

@@

% \cite{goodfellow2016deep} % needed?

>>>>

\documentclass{article}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}
\title{A Graph-based Framework for Coverage Analysis in Autonomous Driving}
\author{xxx}
\date{\today}

@@

test4

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/subgraph_isomorphism_carla_coverage_barchart.png}
    \caption{Coverage barchart for the manually defined coverage scenarios for CARLA.}
    \label{fig:carla_coverage_barchart_manual_scenarios}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/subgraph_isomorphism_agreement_matrix_manual_scenarios_carla.png}
    \caption{Agreement matrix for manually defined coverage scenarios for CARLA.}
    \label{fig:carla_coverage_barchart_manual_scenarios}
\end{figure}

\begin{table}[htbp]
    \caption{My Table}
    \label{tab:mytable}
    \begin{tabular}{rrrrr}
    \toprule
    scn 1 & scn 2 & scn 3 & scn 4 & size \\
    \midrule
    False & False & False & False & 613 \\
    False & False & True & False & 3 \\
    True & True & False & True & 377 \\
    True & True & True & True & 7 \\
    \bottomrule
    \end{tabular}
\end{table}
% \cite{goodfellow2016deep} % needed?
